\documentclass[8pt,a4paper]{moderncv}

% Themes
\moderncvstyle{casual}
\moderncvcolor{blue}
\usepackage[scale=0.8, top=1cm, bottom=3cm]{geometry}

% Personal data
\firstname {Kevin}
\lastname {Hwang}
\title{Software Engineer}
\address{1945 Milvia St. 302}{Berkeley, CA 94704}
\phone[mobile]{(909)~802~8999}
\email{k3vinhwang@gmail.com}
\homepage{www.kevinhwang.net}
\social[linkedin]{k3vinhwang}
\social[twitter]{k3vinhwang}
\social[github]{khwang}

\begin{document}
\makecvtitle

\vspace*{-2\baselineskip}

\section{Education}
%\cventry{2009 to 2012}{Bachelor of Science in Electrical Engineering and Computer Sciences}{University of California Berkeley}{\textit{Grade}}{Description}
\cventry{2009-2012}{Bachelor of Science in Electrical Engineering and Computer Sciences}{University of California, Berkeley}{Berkeley}{}{Overall GPA: 3.385}

\section{Work}
\cventry{Summer 2012-Present}{Scribd, Inc.}{Software Engineer}{San Francisco}{}{As a generalist, I work on projects touching all aspects of the codebase.}

\cventry{Summer 2011}{University of California, Berkeley}{Undergraduate Teaching Assistant}{Berkeley}{}{I instructed students in the introductory course in computer science by leading a discussion section and a lab section. I also wrote and graded the exams.}

\section{Projects}
\cventry{September 2012}{Strawberry}{A music visualizer utilizing the HTML5 Audio API and ThreeJS, for WebGL. Third place winner at HackJam Fall 2012}{}{}{\url{https://github.com/khwang/strawberry}}

\cventry{April 2012}{Gala}{Learn to program by commanding an army of robots in space. Built for the Y Combinator Summer 2012 interview}{}{}{\url{https://github.com/khwang/gala}}

\cventry{February 2011}{Currant}{Collaborative reading with video. Upload an epub and read together}{}{}{\url{https://github.com/khwang/currant}}

\cventry{November 2011}{Write Better With Us}{Use machine learning and natural language processing to improve your writing}{}{}{\url{https://github.com/AjayTripathy/kiwi}}

\cventry{September 2011}{DJS}{A real-time media distribution framework built on top of NodeJS and NowJS. Fourth place winner at Yahoo! Hack}{}{}{\url{https://github.com/khwang/DJS}}

\section{Activities}

\cventry{}{Eta Kappa Nu Honors Society}{Electrical and computer engineering honor society.}{}{}{}

\cventry{}{Computer Science Undergraduate Association}{}{}{}{}

\cventry{}{Lindy on Sproul}{Swing dancing instructor, performer, and website coordinator}{}{}{}

\cventry{}{Hackers at Berkeley}{Founding officer for a club that promotes hacking culture}{}{}{}

\cventry{}{Berkeley Dancer's Den}{Web Designer}{}{}{}

\section{Skills}
\cventry{}{Languages}{}{}{}{\begin{itemize}
		\item Preferred: Javascript, Python, HTML5/CSS3, Scheme, Ruby
		\item Familiarity: CoffeeScript, Java, C, C++
	\end{itemize}}{}
	
\cventry{}{Frameworks}{}{}{}{NodeJS, Socket.IO, jQuery, Web.py, Ruby on Rails}{}
\end{document}

\vspace*{-2\baselineskip}